\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-13 papers/itsc_2012/final.tex
reservation policy now preempts greedy cycles (haven't proven this helps yet)
scenario saving/loading so everything can be easelessly resimulated
amping up results script to make comparisons

AORTA's implementation uses Scala, a language implemented on the Java Virtual
Machine. Scala provides the advantage of functional programming constructs while
still permitting imperative style. Parts of AORTA, including extensions and
clients, can easily be written in Java or Scala. The software, designed for
extensibility, has a documented API, is
open-source\footnote{http://code.google.com/p/road-rage}, and contains all of
the code for the experiments described in Section \ref{sec:results}.

@@

@@

The speed of simulation depends on the step duration $dt$, the map size, and the
number of agents. A measure independent of these factors is the number of agent
steps per second. On a $2.4$ GHz machine, this can be observed to average at
about $150,000$, a number comparable to existing simulators \cite{SUMOthesis}.
Further optimizations are planned.

@@

  autonomous reservation: the greedy approach is a bit wretched. either time
  out, or somehow count how many people are on lanes in the queued groups.
  ideally we'd even recurse and factor in

@@

>>>>

AORTA's implementation uses Scala, a language implemented on the Java Virtual
Machine. Scala provides the advantage of functional programming constructs while
still permitting imperative style. Parts of AORTA, including extensions and
clients, can easily be written in Java or Scala. The software is
open-source\footnote{http://code.google.com/p/road-rage} and easily extensible.
The stop sign policy used in Section \ref{sec:results}'s experiments is
implemented in just $70$ lines of code.

@@

% TODO in fact, this is caused by lack of lane changing!!!
% but that's scary... bad routes really do cause it.

@@

The speed of simulation depends on the step duration $dt$, the map size, and the
number of agents. A measure independent of these factors is the number of agent
steps per second. On a $2.4$ GHz machine, this can be observed to average at
about $150,000$, a number comparable to existing simulators \cite{SUMOthesis}.
When $dt = 0.1$ seconds, this means $15,000$ agents can be comfortably simulated
in real-time.  Further optimizations are planned.

\commentd{if i have a day after the paper's done, I can make this number
better.}

@@

  autonomous reservation: the greedy approach has a timeout, but ideally we'd
  ount how many people are on lanes in the queued groups.  and recurse and
  factor in all agents "dependent" on something

@@

map:

contunuous gen, 1 new /sec. so stabe agent num is testament to policy.

stop sign: stable around 800
signal: noticed one side can be starved for a long time. even when it's their
        cycle, theres no room in the first guy's dest lane, so they all waste the cycle.
        stable around 1200.
reservation: stable around 400. nobody's ever stopping.
